\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-12-07 projects/project_5/molecular_dynamics/article/article.tex
introduction finished

\section{Introduction}
\label{sec:introduction}
    Molecular dynamics (referred to as MD), deals with the time evolution of a
    system of particles, typically atoms or molecules. Being first explored in
    the late 1950's, it has had a wide range of applications, in fields as
    materials science, biochemistry and biophysics. Some of the more pioneering
    works in molecular dynamics are often found in the study of chemical
    physics and more specifically proteins.  In 1975, Levitt and Warshel
    \cite{folding} simulated protein folding and in 1976 Cooper
    \cite{thermoprotein} presented results on thermodynamic fluctuations in
    protein folding with methods comparable to todays standards.

    In order to verify the molecular dynamics model one can for instance
    compare with physical experiments. For molecular systems one particular
    method is of special interest, namely nuclear magnetic resonance
    spectroscopy.

    Molecular Dynamics can take on many forms. Notable in the addition of what
    we examine in this project, is the Monte-Carlo and Brownian dynamics
    variants of MD.

    It is based on the simple idea of considering a finite number of molecules
    and letting them interact for a fixed amount of time, which gives us an
    idea of how the system evolves.

    In this project we examine what goes into creating a working MD-program
    that can compute various physical quantities and then proceed by
    considering some specific systems where we look at, amongst other, the
    kinetic energy, the initial temperature required in order to reach a
    desired final temperature, and finding the diffusion constant for the
    system in order to compute the melting temperature.

@@

\begin{thebibliography}{9}
\bibitem{folding}
    Levitt, M., \& Warshel, A., `Computer simulation of protein folding`, Nature, Vol. 253, No. 5494. Available from: \url{http://csb.stanford.edu/levitt/Levitt_NAT75_folding.pdf}
\bibitem{thermoprotein}
    Cooper, A. `Thermodynamic fluctuations in protein molecules`, Proceedings of the National Academy of Sciences of the United States of America, Vol. 73, No. 8. Available from: \url{http://www.pnas.org/content/73/8/2740.full.pdf}
\bibitem{min_image}
    \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions#Practical_implementation:_continuity_and_the_minimum_image_convention}
\bibitem{equipar} \url{https://en.wikipedia.org/wiki/Equipartition\_theorem}
\bibitem{virial} \url{https://en.wikipedia.org/wiki/Virial_theorem}
\end{thebibliography}
\end{document}

>>>>

\section{Introduction}
\label{sec:introduction}

    Molecular dynamics (referred to as MD), deals with the time evolution of a
    system of particles, typically atoms or molecules. Being first explored in
    the late 1950's, it has had a wide range of applications, in fields as
    materials science, biochemistry and biophysics. Some of the more pioneering
    works in molecular dynamics are often found in the study of chemical
    physics and more specifically proteins.  In 1975, Levitt and Warshel
    \cite{folding} simulated protein folding and in 1976 Cooper
    \cite{thermoprotein} presented results on thermodynamic fluctuations in
    protein folding with methods comparable to todays standards. More related
    to our project are the results of A. Rahman in 1964 \cite{liquid_argon}
    where he simulates liquid argon and find his simulations to more or less
    agree with experiments.

    In order to verify the molecular dynamics model one can for instance
    compare with physical experiments. For molecular systems one particular
    method is of special interest, namely nuclear magnetic resonance
    spectroscopy.  Molecular Dynamics can take on many forms. Notable in the
    addition to what we examine in this project, is the Monte-Carlo and
    Brownian dynamics variants of MD.

    Molecular dynamics is based on the simple idea of considering a finite
    number of molecules and letting them interact for a fixed amount of time,
    which gives us an idea of how the system evolves.  In this project we
    examine what goes into creating a working MD-program that can compute
    various physical quantities and then proceed by considering some specific
    systems where we look at, amongst other, the kinetic energy, the initial
    temperature required in order to reach a desired final temperature, and
    finding the diffusion constant for the system in order to compute the
    melting temperature.

@@

\begin{thebibliography}{9}
\bibitem{folding}
    Levitt, M., \& Warshel, A., `Computer simulation of protein folding`, Nature, Vol. 253, No. 5494. Available from: \url{http://csb.stanford.edu/levitt/Levitt_NAT75_folding.pdf}
\bibitem{thermoprotein}
    Cooper, A. `Thermodynamic fluctuations in protein molecules`, Proceedings of the National Academy of Sciences of the United States of America, Vol. 73, No. 8. Available from: \url{http://www.pnas.org/content/73/8/2740.full.pdf}
\bibitem{liquid_argon}
    Rahman, A., `Correlations in the Motion of Atoms in Liquid Argon`, Physical Review, Volume 136, No. 2A. Available from: \url{http://journals.aps.org/pr/pdf/10.1103/PhysRev.136.A405}.
\bibitem{min_image}
    `Periodic boundary conditions` (wiki article), December 7, 2015. Available from: \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions#Practical_implementation:_continuity_and_the_minimum_image_convention} [November 13, 2015]
\bibitem{equipar} 
    `Equipartition theorem` (wiki article), December 7, 2015.
    Available from: \url{https://en.wikipedia.org/wiki/Equipartition\_theorem} [November 21, 2015]
\bibitem{virial} 
    `Virial theorem` (wiki article), December 7, 2015, \url{https://en.wikipedia.org/wiki/Virial_theorem} [October 7, 2015]
\end{thebibliography}
\end{document}
